Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
z plus update

KHMM uses k-means clustering to discretize the space of real vectors followed by training one Hidden Markov Model for each gesture type.  The intuition behind this can be thought of as follows: the clustering across all gesture types serves mainly to project each data vector which is in $ \mathbb{R}^n $ (where there are $n$ features) to $\mathbb{Z}$.  Concretely this discretizes the data uniformly regardless of what gesture type it belongs to.  Following the discretization KHMM then trains a Hidden Markov Model of the discretized training sets for each gesture type.
\\
\\
Formally we describe the algorithm as follows:

	\subsubsection{Clustering}
		For all training example across all gesture types, kmeans defines a clustering function $f: \mathbb{R}^n \rightarrow \mathbb{Z}$. 
	\subsubsection{Hidden Markov Model}
		For each set of training examples for each gesture type train a Hidden Markov Model.  Namely in this stage, for each gesture type $g$, we generate a function $h_g: (\mathbb{Z}^k) \rightarrow \mathbb{R}_{[0,1]}$  by the Hidden Markov Model process:
$HMM: (\mathbb{Z}^k)^t \rightarrow h_g$, where each training example consists of $k$ instantaneous data points and there are $t$ training examples for gesture type g.  
	\subsubsection{Classification Procedure}
		To classify an unknown gesture example, which exists in $(\mathbb{R}^n)^k$, we first transform it to its discretized version, namely $f(\mathbb{R}^n)^k$ and then for each gesture type $g$, apply $h_g((f(\mathbb{R}^n))^k)$ and classify the example according to the $g’$ were $h_g’$ returns maximum value.

@@

	\subsubsection{Clustering}
		For each gesture type $g$ across all training examples, kmeans defines a clustering function $f_g: \mathbb{R}^n \rightarrow \mathbb{Z}$.
	\subsubsection{Hidden Markov Model}
		For each set of training examples for each gesture type train a Hidden Markov Model.  Namely in this set we generate a function $h_g: (\mathbb{Z}^k) \rightarrow \mathbb{R}_{[0,1]}$ by the Hidden Markov Model process: 
		$HMM: (\mathbb{Z}^k)^t \rightarrow h_g$, where each training example consists of $k$ instantaneous data points and there are $t$ training examples for gesture type $g$.

@@

		\subsubsection{Clustering}
		For each gesture type $g$ across all training examples, kmeans defines a clustering function $f_g: \mathbb{R}^n \rightarrow \mathbb{Z}$.

>>>>

KHMM uses k-means clustering to discretize the space of real vectors followed by training one Hidden Markov Model for each gesture type.  The intuition behind this can be thought of as follows: the clustering across all gesture types serves mainly to project each data vector which is in $ \mathbb{R}^n $ (where there are $n$ features) to $\mathbb{Z^{+}}$.  Concretely this discretizes the data uniformly regardless of what gesture type it belongs to.  Following the discretization KHMM then trains a Hidden Markov Model of the discretized training sets for each gesture type.
\\
\\
Formally we describe the algorithm as follows:

	\subsubsection{Clustering}
		For all training example across all gesture types, kmeans defines a clustering function $f: \mathbb{R}^n \rightarrow \mathbb{Z^{+}}$. 
	\subsubsection{Hidden Markov Model}
		For each set of training examples for each gesture type train a Hidden Markov Model.  Namely in this stage, for each gesture type $g$, we generate a function $h_g: (\mathbb{Z^{+}}^k) \rightarrow \mathbb{R}_{[0,1]}$  by the Hidden Markov Model process:
$HMM: (\mathbb{Z^{+}}^k)^t \rightarrow h_g$, where each training example consists of $k$ instantaneous data points and there are $t$ training examples for gesture type g.  
	\subsubsection{Classification Procedure}
		To classify an unknown gesture example, which exists in $(\mathbb{R}^n)^k$, we first transform it to its discretized version, namely $f(\mathbb{R}^n)^k$ and then for each gesture type $g$, apply $h_g((f(\mathbb{R}^n))^k)$ and classify the example according to the $g’$ were $h_g’$ returns maximum value.

@@

	\subsubsection{Clustering}
		For each gesture type $g$ across all training examples, kmeans defines a clustering function $f_g: \mathbb{R}^n \rightarrow \mathbb{Z^{+}}$.
	\subsubsection{Hidden Markov Model}
		For each set of training examples for each gesture type train a Hidden Markov Model.  Namely in this set we generate a function $h_g: (\mathbb{Z^{+}}^k) \rightarrow \mathbb{R}_{[0,1]}$ by the Hidden Markov Model process: 
		$HMM: (\mathbb{Z^{+}}^k)^t \rightarrow h_g$, where each training example consists of $k$ instantaneous data points and there are $t$ training examples for gesture type $g$.

@@

		\subsubsection{Clustering}
		For each gesture type $g$ across all training examples, kmeans defines a clustering function $f_g: \mathbb{R}^n \rightarrow \mathbb{Z^{+}}$.
